\textbf{Computational Fuzzy Extractors}

### 2013-06-14 CompFuzzExt.tex
updated Lem 4.4 to match DMQ13 Cor. 1

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

@@

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime. The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$. If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is secure.
\end{lemma}

@@

%\begin{lemma}
%\label{lem:conversion to unpredictability}
%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
%\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} as long as all the parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.  
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

%\subsection{Computational Secure Sketch based on \class{LWE}}
%\label{subsec:fuzzyExtLWE}
%We now give a formal description of our sketch based on LWE.  We now consider a source $W$~(this fulfills the role of $E$ in standard LWE notation):
%
%\begin{construction}[Computation Secure Sketch based on LWE]
%\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.  Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+3\gamma}m$.  Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.  Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.  Then the following is a computational secure sketch:%We present the construction in 
%%\begin{figure}
%%\label{fig:construction figure}
%%\caption{Computational Secure Sketch based on the Learning with Errors problem}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\vA\in\Fq^{m\times n}, x\in\Fq^n$ uniformly.
%\item Output $p = (\vA, \vA x+w)$.\\
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p)$
%\item Parse $p$ as $(\vA, \vect{C})$
%\item Set $x' = \decode_t(\vA, \vect{C}-w') $. 
%\item Output $w = \vect{C}-\vA x'$.
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
%%\end{figure}
%%\textbf{\gen}
%%\begin{enumerate}
%%\item Input $w\leftarrow W$.
%%\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
%%\item Use $w$ as the randomness for the sampling algorithm, \\$\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
%%\item Output $p = (A, AX+E)$.
%%\end{enumerate}
%%
%%
%%\textbf{\rep}
%%\begin{enumerate}
%%\item Input $(w', p)$
%%\item Parse $p$ as $(A, C)$
%%\item Compute $E' \leftarrow \sample (w')$.
%%\item Set $X' = \decode_t(A, C-E') $. 
%%\item Output $sam_w = C-AX'$.
%%\end{enumerate}
%\end{construction}

@@

\newpage
\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
\item If $B- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.    Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, bm, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.  Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
 there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$. The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
\end{theorem}

@@

\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.

@@

\rho q  &= 2n^{1/2+3\gamma}m\\

@@

Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:

@@

m \log 2n^{1/2+3\gamma}m &= k \log n^f

@@

%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}

@@

f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma} m}{\log n}

@@

f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+3\gamma}}{\log n}

@@

%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+3\gamma}}{\log n}$}

@@

q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}

>>>>

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $Z^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.  Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

@@

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime (unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding). The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 1]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime and $m = m(n) = \poly(n)$ be an integer with $m\ge 3n$. Let $\sigma \in (0, 1)$ be an arbitrarily small  constant and let $\rho=\rho(n)\in (0,1/10)$ be such that $\rho q \geq 2n^{1/2+\sigma}m$. If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard within a factor of $\tilde{O}(n^{1+\sigma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$,  $\distLWE_{n, m, q, \chi}$ is secure.
\end{lemma}

@@

%\begin{lemma}
%\label{lem:conversion to unpredictability}
%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
%\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+\sigma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+\sigma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
The security of  \consref{cons:informal construction} follows from Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} as long as all the parameters are set appropriately (see \thref{thm:lossless secure extractor log}),  because we use the hardcore bits of $X$ as our key.  
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

%\subsection{Computational Secure Sketch based on \class{LWE}}
%\label{subsec:fuzzyExtLWE}
%We now give a formal description of our sketch based on LWE.  We now consider a source $W$~(this fulfills the role of $E$ in standard LWE notation):
%
%\begin{construction}[Computation Secure Sketch based on LWE]
%\label{cons:LWESecureSketch} Let $n$ be a security parameter and let $m = m(n) = \poly(n), q = q(n)\geq 2$ be integers.  Let $\gamma\in (0,1)$ be a constant and let $\rho \in (0,1)$ such that $\rho q\geq 2n^{1/2+\sigma}m$.  Let $\decode_t$ be an algorithm~(not necessarily efficient) that inverts an LWE instance when no more than $t$ of $m$ dimensions have non-zero error.  Let $W$ be a distribution over $\{0,1\}^{(\log \rho q)\times m}$\,.  Then the following is a computational secure sketch:%We present the construction in 
%%\begin{figure}
%%\label{fig:construction figure}
%%\caption{Computational Secure Sketch based on the Learning with Errors problem}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\vA\in\Fq^{m\times n}, x\in\Fq^n$ uniformly.
%\item Output $p = (\vA, \vA x+w)$.\\
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p)$
%\item Parse $p$ as $(\vA, \vect{C})$
%\item Set $x' = \decode_t(\vA, \vect{C}-w') $. 
%\item Output $w = \vect{C}-\vA x'$.
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
%%\end{figure}
%%\textbf{\gen}
%%\begin{enumerate}
%%\item Input $w\leftarrow W$.
%%\item Sample $A\in\Fq^{m\times n}, x\in\Fq^n$ uniformly at random.
%%\item Use $w$ as the randomness for the sampling algorithm, \\$\sample$, for $\chi$.  Set $E\leftarrow  \sample(w)$.
%%\item Output $p = (A, AX+E)$.
%%\end{enumerate}
%%
%%
%%\textbf{\rep}
%%\begin{enumerate}
%%\item Input $(w', p)$
%%\item Parse $p$ as $(A, C)$
%%\item Compute $E' \leftarrow \sample (w')$.
%%\item Set $X' = \decode_t(A, C-E') $. 
%%\item Output $sam_w = C-AX'$.
%%\end{enumerate}
%\end{construction}

@@

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
\item If $B- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.    Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z=[-2^{b-1}+1,2^{b-1}]$ of size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds: \consref{cons:informal construction} is a $(\M, W, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet $Z$ of size $2^b$, where the block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.  Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $\mathcal{W}$ be the class of all $m$-symbol fixing sources over $\zo^{(m+\alpha)b}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
 there exists $\epsilon = \ngl(n)$ 
such that the following holds: \consref{cons:informal construction} is a $(\M, \mathcal{W}, bm, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
 The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
\end{theorem}

@@

\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + \sigma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+\sigma}m$.

@@

\rho q  &= 2n^{1/2+\sigma}m\\

@@

Substituting $q = n^f$ and $\rho q = 2n^{1/2+\sigma}m$ yields the following system of equations:

@@

m \log 2n^{1/2+\sigma}m &= k \log n^f

@@

%\xnote{$ m \log 2n^{1/2+\sigma}m = n \log n^f$}

@@

f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma} m}{\log n}

@@

f &= \frac{m}{k}\frac{\log 2n^{1/2+\sigma}m}{\log n} = \frac{g(c+2d)}{d}\frac{\log \frac{2(c+2d)}{d} n^{3/2+\sigma}}{\log n}

@@

%\xnote{$f = \frac{m}{n}\frac{\log 2n^{1/2+\sigma}m }{\log n} = \frac{c+d}{d}\frac{\log 2(c+d)/d n^{3/2+\sigma}}{\log n}$}

@@

q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+\sigma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+\sigma}m = \frac{2(c+2d)n^{3/2+\sigma}}{d}
